---
title: "Filtering"
author: "Kaylee Arnold"
date: "5/10/2022"
output: html_document
---


#Import
Call phyloseq from Import.R
```{r eval=FALSE, include=FALSE}

#source("2_Import.R")
```

#Prune reads
Prune to over 2133 reads, based on alpha rarefaction (double check rarefaction values)
```{r include=FALSE}
pruned_phyloseq <- sum(sample_sums(phyloseq) == 0) #we start with 355 samples (all guts)

pruned_phyloseq <- prune_samples(sample_sums(phyloseq) > 0, phyloseq)

pruned_phyloseq <- prune_samples(sample_sums(pruned_phyloseq) > 2132, pruned_phyloseq) #335 samples


any(sample_sums(pruned_phyloseq) == 2132)
```

#Filtering taxa

Look at all taxa from beginning -
##Filter out non-bacteria (archaea, unassigned kingdoms)
```{r include=FALSE}

table(tax_table(pruned_phyloseq)[,"Kingdom"], exclude = NULL) #Look at all Kingdoms from beginning

filtering <- subset_taxa(pruned_phyloseq, !is.na(Kingdom) & !Kingdom %in% c("", "Unassigned")) #filter out Unassigned Kingdoms

table(tax_table(filtering)[,"Kingdom"], exclude = NULL) #check which Kingdoms are left after filtering

filterKingdom = c("Archaea") #filter out archaea

filtering = subset_taxa(filtering, !Kingdom %in% filterKingdom) # filter out Archaea

table(tax_table(filtering)[,"Kingdom"], exclude = NULL) #check which Kingdoms are left after filtering -- should only have bacteria left

```


##Remove Chloroplast (but not NAs)
```{r include=FALSE}
filterClass = ("Chloroplast") # Filter out chloroplasts
classfilter = subset_taxa(filtering, !Class %in% filterClass) #no chloroplasts, NAs included

table(tax_table(classfilter)[, "Class"], exclude = NULL) #check which classes are left after filter (NAs included)
```

##Remove mitochondria (but not NAs)
```{r include=FALSE}

filterFamily = ("mitochondria")
family_filter = subset_taxa(classfilter, !Family %in% filterFamily)
table(tax_table(family_filter)[, "Family"], exclude = NULL) #check to make sure mitochondria were removed

```



##Remove Wolbachia from all samples
```{r include=FALSE}
filterWolbachia = ("Wolbachia")
# Filter entries with unidentified Phylum.
wolbachia_filter = subset_taxa(family_filter, !Genus %in% filterWolbachia)

table(tax_table(wolbachia_filter)[, "Genus"], exclude = NULL) #check to make sure Wolbachia is removed

```

Examine all ASVs
```{r include=FALSE}
tax_table_species <- table(tax_table(wolbachia_filter)[, "Species"], exclude = NULL)
```


#Rename cleaned phyloseq object
```{r include=FALSE}
phyloseq_cleaned <- wolbachia_filter #rename (final phyloseq object has NAs in phyla and lower taxa levels, but no Chloroplasts, mitochondria, or wolbachia)

```

