---
title: "Abundance_clean_2023"
author: "Kaylee Arnold"
date: "2023-02-22"
output: html_document
---

This document creates relative abundance figures

#Phylum
##All samples
Prune to top 20 phyla - using rpal_field
```{r}

top10P.names = sort(tapply(taxa_sums(rpal_field_BM), tax_table(rpal_field_BM)[, "Phylum"], sum), TRUE)[1:10]
#Cut down the physeq.tree data to only the top 10 Genus
top10P = subset_taxa(rpal_field, Phylum %in% names(top10P.names)) #new phyloseq object at top 20 genera

```

###Convert to relative abundance
```{r}
ps_phylum <- top10P %>%
  tax_glom(taxrank = "Phylum") %>%                     # agglomerate at genus level
  transform_sample_counts(function(x) {x/sum(x)} ) %>% # Transform to rel. abundance
  psmelt() %>%                                         # Melt to long format
  filter(Abundance > 0.01) %>%                         # Filter out low abundance taxa
  arrange(Phylum) 
```

###Re-Set color scale for graph
```{r}
#display.brewer.all(n=NULL, type="all", select=NULL, exact.n=TRUE,
#colorblindFriendly=TRUE)

colourCount <- 10 # max number of categories you need (10 because we are looking at top 10 genera)
getPalette <- colorRampPalette(brewer.pal(10, "Paired")) # 10 is for the number of distinct colors to use, and 12 is the most for "Paired"

```

###All Samples
####Relative abundance of top 10 genus 
```{r}

phyla_barplot <- ggplot(ps_phylum, aes(x = Sample_Name, y = Abundance, fill = Phylum)) + 
  geom_bar(stat = "identity", position = "fill", width = .8) + #width is individual bar width
  scale_fill_manual(values = getPalette(colourCount)) +
  # Remove x axis title and axis ticks
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
  theme(panel.border = element_blank(),
    panel.background = element_blank()) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  #scale_color_manual(breaks=c('Sphingomonas', 'Erwinia', 'Stenotrophomonas', 'Delftia', "Dietzia", "Staphylococcus", "Pseudomonas", "Corynebacterium", "Enterobacter", "Streptococcus")) +
  labs(x = 'Samples', y = "Relative Abundance", fill = "Top Phyla") +
  ggtitle("Genera Composition Across Samples") 
  #theme(legend.position = "none")
```


#Genus Relative Abundance
##All samples, Region, and Habitat
Prune to top 20 genera - using rpal_field
```{r}

top10G.names = sort(tapply(taxa_sums(rpal_field), tax_table(rpal_field)[, "Genus"], sum), TRUE)[1:10]
#Cut down the physeq.tree data to only the top 10 Genus
top10G = subset_taxa(rpal_field, Genus %in% names(top10G.names)) #new phyloseq object at top 20 genera

```

###Convert to relative abundance
```{r}
ps_genus <- top10G %>%
  tax_glom(taxrank = "Genus") %>%                     # agglomerate at genus level
  transform_sample_counts(function(x) {x/sum(x)} ) %>% # Transform to rel. abundance
  psmelt() %>%                                         # Melt to long format
  filter(Abundance > 0.01) %>%                         # Filter out low abundance taxa
  arrange(Genus) 
```

###Re-Set color scale for graph
```{r}
#display.brewer.all(n=NULL, type="all", select=NULL, exact.n=TRUE,
#colorblindFriendly=TRUE)

colourCount <- 10 # max number of categories you need (10 because we are looking at top 10 genera)
getPalette <- colorRampPalette(brewer.pal(10, "Paired")) # 10 is for the number of distinct colors to use, and 12 is the most for "Paired"

```

###All Samples
####Relative abundance of top 10 genus 
```{r}

ggplot(ps_genus, aes(x = Sample_Name, y = Abundance, fill = Genus)) + 
  geom_bar(stat = "identity", position = "fill", width = 1) + #width is individual bar width
  scale_fill_manual(values = getPalette(colourCount)) +
  # Remove x axis title and axis ticks
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
  theme(panel.border = element_blank(),
    panel.background = element_blank()) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  scale_color_manual(breaks=c('Sphingomonas', 'Erwinia', 'Stenotrophomonas', 'Delftia', "Dietzia", "Staphylococcus", "Pseudomonas", "Corynebacterium", "Enterobacter", "Streptococcus")) +
  labs(x = 'Samples', y = "Relative Abundance", fill = "Top 10 Genera") +
  ggtitle("Genera Composition Across Samples") 
  #theme(legend.position = "none")
```

####Count data for top 10 genera
```{r}
TGroup <- tax_glom(top10G, taxrank = "Genus")
PGroup <- transform_sample_counts(TGroup, function(x)100* x / sum(x))
OTUg <- otu_table(PGroup)
TAXg <- tax_table(PGroup)[,"Genus"]
AverageD <- as.data.frame(rowMeans(OTUg))
names(AverageD) <- c("Mean")
GTable <- merge(TAXg, AverageD, by=0, all=TRUE)
GTable$Row.names = NULL
GTable <- GTable[order(desc(GTable$Mean)),]
head(GTable)
```


#Species level
```{r}

################
# to view all species, not just the top ones

ALLSpecies.names = sort(tapply(taxa_sums(rpal_field), tax_table(rpal_field)[, "Species"], sum), TRUE)

#Cut down the physeq.tree data to only the top 20 species
ALLSpecies = subset_taxa(rpal_field, Species %in% names(ALLSpecies.names)) #new phyloseq object at top 20 ASVs

#######################

top10S.names = sort(tapply(taxa_sums(rpal_field), tax_table(rpal_field)[, "Species"], sum), TRUE)[1:10]
#Cut down the physeq.tree data to only the top 10 species
top10S = subset_taxa(rpal_field, Species %in% names(top10S.names)) #new phyloseq object at top 20 ASVs

```

###Convert to relative abundance
```{r}

##### for all species, not just top ones
ps_species_ALL <- ALLSpecies %>%
  tax_glom(taxrank = "Species") %>%                     # agglomerate at species level
  transform_sample_counts(function(x) {x/sum(x)} ) %>% # Transform to rel. abundance
  psmelt() %>%                                         # Melt to long format
  filter(Abundance > 0.01) %>%                         # Filter out low abundance taxa
  arrange(Species)

###########

ps_species <- top10S %>%
  tax_glom(taxrank = "Species") %>%                     # agglomerate at species level
  transform_sample_counts(function(x) {x/sum(x)} ) %>% # Transform to rel. abundance
  psmelt() %>%                                         # Melt to long format
  filter(Abundance > 0.01) %>%                         # Filter out low abundance taxa
  arrange(Species) 
```

write out csv of ASV table for species of all samples
```{r}
write_csv(ps_species_ALL, "ASV_Table_allSpecies.csv")

```


###Re-Set color scale for graph
```{r}
#display.brewer.all(n=NULL, type="all", select=NULL, exact.n=TRUE,
#colorblindFriendly=TRUE)

colourCount <- 10 # max number of categories you need (10 because we are looking at top 10 genera)
getPalette <- colorRampPalette(brewer.pal(10, "Paired")) # 10 is for the number of distinct colors to use, and 12 is the most for "Paired"

```

###All Samples
####Relative abundance of top 10 genus 
```{r}

species_barplot <- ggplot(ps_species, aes(x = Sample_Name, y = Abundance, fill = Species)) +
  geom_bar(stat = "identity", position = "fill") + #width is individual bar width
  scale_fill_manual(values = getPalette(colourCount)) +
  # Remove x axis title and axis ticks
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
  theme(panel.border = element_blank(),
    panel.background = element_blank()) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  scale_color_manual(breaks=c('Sphingomonas', 'Erwinia', 'Stenotrophomonas', 'Delftia', "Dietzia", "Staphylococcus", "Pseudomonas", "Corynebacterium", "Enterobacter", "Streptococcus")) +
  labs(x = 'Samples', y = "Relative Abundance", fill = "Top 10 Genera") +
  ggtitle("Genera Composition Across Samples")
  #theme(legend.position = "none")
```

####Count data for top 20 species
```{r}
TGroup <- tax_glom(top20S, taxrank = "Species")
PGroup <- transform_sample_counts(TGroup, function(x)100* x / sum(x))
OTUg <- otu_table(PGroup)
TAXg <- tax_table(PGroup)[,"Species"]
AverageD <- as.data.frame(rowMeans(OTUg))
names(AverageD) <- c("Mean")
GTable <- merge(TAXg, AverageD, by=0, all=TRUE)
GTable$Row.names = NULL
GTable <- GTable[order(desc(GTable$Mean)),]
head(GTable)
```

##Region

Plot - species
```{r}

ggplot(ps_species, aes(x = Sample_Name, y = Abundance, fill = Species)) + 
  facet_wrap(~Region, scales = "free_x") +
  geom_bar(stat = "identity", position = "fill", width = 1) + #width is individual bar width
  scale_fill_manual(values = getPalette(colourCount)) +
  # Remove x axis title and axis ticks
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
  theme(panel.border = element_blank(),
    panel.background = element_blank()) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  scale_color_manual(breaks=c('Sphingomonas', 'Erwinia', 'Stenotrophomonas', 'Delftia', "Dietzia", "Staphylococcus", "Pseudomonas", "Corynebacterium", "Enterobacter", "Streptococcus")) +
  labs(x = 'Samples', y = "Relative Abundance", fill = "Top 10 ASVs") +
  ggtitle("ASV Composition Across Samples")
  #theme(legend.position = "none")
```


##Habitat


Plot - species
```{r}

ggplot(ps_species, aes(x = Sample_Name, y = Abundance, fill = Species)) + 
  facet_wrap(~HABITAT, scales = "free_x") +
  geom_bar(stat = "identity", position = "fill", width = 1) + #width is individual bar width
  scale_fill_manual(values = getPalette(colourCount)) +
  # Remove x axis title and axis ticks
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
  theme(panel.border = element_blank(),
    panel.background = element_blank()) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  scale_color_manual(breaks=c('Sphingomonas', 'Erwinia', 'Stenotrophomonas', 'Delftia', "Dietzia", "Staphylococcus", "Pseudomonas", "Corynebacterium", "Enterobacter", "Streptococcus")) +
  labs(x = 'Samples', y = "Relative Abundance", fill = "Top 10 Genera") +
  ggtitle("Genera Composition Across Samples")
  #theme(legend.position = "none")
```

##Infection

```{r}

ggplot(ps_species, aes(x = Sample_Name, y = Abundance, fill = Species)) + 
  facet_wrap(~SingleInf_Tcruzi, scales = "free_x") +
  geom_bar(stat = "identity", position = "fill", width = 1) + #width is individual bar width
  scale_fill_manual(values = getPalette(colourCount)) +
  # Remove x axis title and axis ticks
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
  theme(panel.border = element_blank(),
    panel.background = element_blank()) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  scale_color_manual(breaks=c('Sphingomonas', 'Erwinia', 'Stenotrophomonas', 'Delftia', "Dietzia", "Staphylococcus", "Pseudomonas", "Corynebacterium", "Enterobacter", "Streptococcus")) +
  labs(x = 'Samples', y = "Relative Abundance", fill = "Top 10 Genera") +
  ggtitle("Genera Composition Across Samples")
  #theme(legend.position = "none")
```

##PalmID
```{r}

ggplot(ps_species, aes(x = PalmID, y = Abundance, fill = Species)) + 
  facet_wrap(~HABITAT, scales = "free_x") +
  geom_bar(stat = "identity", position = "fill", width = 1) + #width is individual bar width
  scale_fill_manual(values = getPalette(colourCount)) +
  # Remove x axis title and axis ticks
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
  theme(panel.border = element_blank(),
    panel.background = element_blank()) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  scale_color_manual(breaks=c('Sphingomonas', 'Erwinia', 'Stenotrophomonas', 'Delftia', "Dietzia", "Staphylococcus", "Pseudomonas", "Corynebacterium", "Enterobacter", "Streptococcus")) +
  labs(x = 'Samples', y = "Relative Abundance", fill = "Top 10 Genera") +
  ggtitle("Genera Composition Across Samples")
  #theme(legend.position = "none")
```

#Veraguas

```{r}
top10S.names = sort(tapply(taxa_sums(rpal_field_veraguas), tax_table(rpal_field_veraguas)[, "Species"], sum), TRUE)[1:10]
#Cut down the physeq.tree data to only the top 10 Genus
top10S = subset_taxa(rpal_field_veraguas, Species %in% names(top10S.names)) #new phyloseq object at top 20 ASVs

```

Convert to relative abundance
```{r}
ps_species_veraguas <- top10S %>%
  tax_glom(taxrank = "Species") %>%                     # agglomerate at species level
  transform_sample_counts(function(x) {x/sum(x)} ) %>% # Transform to rel. abundance
  psmelt() %>%                                         # Melt to long format
  filter(Abundance > 0.01) %>%                         # Filter out low abundance taxa
  arrange(Species) 
```

Re-Set color scale for graph
```{r}
#display.brewer.all(n=NULL, type="all", select=NULL, exact.n=TRUE,
#colorblindFriendly=TRUE)

colourCount <- 10 # max number of categories you need (10 because we are looking at top 10 genera)
getPalette <- colorRampPalette(brewer.pal(10, "Paired")) # 10 is for the number of distinct colors to use, and 12 is the most for "Paired"

```

###PalmID

```{r}

ggplot(ps_species_veraguas, aes(x = PalmID, y = Abundance, fill = Species)) +
  geom_bar(stat = "identity", position = "fill") + #width is individual bar width
  facet_wrap(~HABITAT, scales = "free_x") +
  scale_fill_manual(values = getPalette(colourCount)) +
  # Remove x axis title and axis ticks
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
  theme(panel.border = element_blank(),
    panel.background = element_blank()) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  labs(x = 'Samples', y = "Relative Abundance", fill = "Top 10 Genera") +
  ggtitle("Genera Composition Across Veraguas")
  #theme(legend.position = "none")
```

###Habitat type
```{r}

ggplot(ps_species_veraguas, aes(x = Sample_Name, y = Abundance, fill = Species)) +
  geom_bar(stat = "identity", position = "fill") + #width is individual bar width
  facet_wrap(~HABITAT, scales = "free_x") +
  scale_fill_manual(values = getPalette(colourCount)) +
  # Remove x axis title and axis ticks
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
  theme(panel.border = element_blank(),
    panel.background = element_blank()) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  labs(x = 'Samples', y = "Relative Abundance", fill = "Top 10 Genera") +
  ggtitle("Genera Composition Across Veraguas")
  #theme(legend.position = "none")
```

###Tcruzi
```{r}

ggplot(ps_species_veraguas, aes(x = Sample_Name, y = Abundance, fill = Species)) +
  geom_bar(stat = "identity", position = "fill") + #width is individual bar width
  facet_wrap(~SingleInf_Tcruzi, scales = "free_x") +
  scale_fill_manual(values = getPalette(colourCount)) +
  # Remove x axis title and axis ticks
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
  theme(panel.border = element_blank(),
    panel.background = element_blank()) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  labs(x = 'Samples', y = "Relative Abundance", fill = "Top 10 Genera") +
  ggtitle("Genera Composition Across Veraguas")
  #theme(legend.position = "none")
```

###Forest Tcruzi

Reset using ony forest samples
```{r}
top10S.names = sort(tapply(taxa_sums(rpal_field_forest), tax_table(rpal_field_forest)[, "Species"], sum), TRUE)[1:10]
#Cut down the physeq.tree data to only the top 10 Genus
top10S = subset_taxa(rpal_field_forest, Species %in% names(top10S.names)) #new phyloseq object at top 20 ASVs

```

Convert to relative abundance
```{r}
ps_species_forest <- top10S %>%
  tax_glom(taxrank = "Species") %>%                     # agglomerate at species level
  transform_sample_counts(function(x) {x/sum(x)} ) %>% # Transform to rel. abundance
  psmelt() %>%                                         # Melt to long format
  filter(Abundance > 0.01) %>%                         # Filter out low abundance taxa
  arrange(Species) 
```

####Plot
```{r}

ggplot(ps_species_forest, aes(x = Sample_Name, y = Abundance, fill = Species)) +
  geom_bar(stat = "identity", position = "fill") + #width is individual bar width
  facet_wrap(~SingleInf_Tcruzi, scales = "free_x") +
  scale_fill_manual(values = getPalette(colourCount)) +
  # Remove x axis title and axis ticks
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
  theme(panel.border = element_blank(),
    panel.background = element_blank()) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  labs(x = 'Samples', y = "Relative Abundance", fill = "Top 10 Genera") +
  ggtitle("Genera Composition Across Veraguas")
  #theme(legend.position = "none")
```

##Capira
Reset using only capira samples
```{r}
top10S.names = sort(tapply(taxa_sums(rpal_field_capira), tax_table(rpal_field_capira)[, "Species"], sum), TRUE)[1:10]
#Cut down the physeq.tree data to only the top 10 Genus
top10S = subset_taxa(rpal_field_capira, Species %in% names(top10S.names)) #new phyloseq object at top 20 ASVs

```

Convert to relative abundance
```{r}
ps_species_capira <- top10S %>%
  tax_glom(taxrank = "Species") %>%                     # agglomerate at species level
  transform_sample_counts(function(x) {x/sum(x)} ) %>% # Transform to rel. abundance
  psmelt() %>%                                         # Melt to long format
  filter(Abundance > 0.01) %>%                         # Filter out low abundance taxa
  arrange(Species) 
```

####Habitat type
```{r}

ggplot(ps_species_capira, aes(x = Sample_Name, y = Abundance, fill = Species)) +
  geom_bar(stat = "identity", position = "fill") + #width is individual bar width
  facet_wrap(~HABITAT, scales = "free_x") +
  scale_fill_manual(values = getPalette(colourCount)) +
  # Remove x axis title and axis ticks
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
  theme(panel.border = element_blank(),
    panel.background = element_blank()) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  labs(x = 'Samples', y = "Relative Abundance", fill = "Top 10 Genera") +
  ggtitle("Genera Composition Across Capira")
  #theme(legend.position = "none")
```

####Tcruzi
```{r}

ggplot(ps_species_capira, aes(x = Sample_Name, y = Abundance, fill = Species)) +
  geom_bar(stat = "identity", position = "fill") + #width is individual bar width
  facet_wrap(~SingleInf_Tcruzi, scales = "free_x") +
  scale_fill_manual(values = getPalette(colourCount)) +
  # Remove x axis title and axis ticks
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
  theme(panel.border = element_blank(),
    panel.background = element_blank()) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  labs(x = 'Samples', y = "Relative Abundance", fill = "Top 10 Genera") +
  ggtitle("Genera Composition Across Veraguas")
  #theme(legend.position = "none")
```

PalmID
```{r}

ggplot(ps_species_capira, aes(x = PalmID, y = Abundance, fill = Species)) +
  geom_bar(stat = "identity", position = "fill") + #width is individual bar width
  #facet_wrap(~PalmID, scales = "free_x") +
  scale_fill_manual(values = getPalette(colourCount)) +
  # Remove x axis title and axis ticks
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
  theme(panel.border = element_blank(),
    panel.background = element_blank()) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  labs(x = 'Samples', y = "Relative Abundance", fill = "Top 10 Genera") +
  ggtitle("Genera Composition Across Capira")
  #theme(legend.position = "none")
```

##Forest
```{r}
top10S.names = sort(tapply(taxa_sums(rpal_Palm_SF10), tax_table(rpal_Palm_SF10)[, "Species"], sum), TRUE)[1:10]
#Cut down the physeq.tree data to only the top 10 Genus
top10S = subset_taxa(rpal_Palm_SF10, Species %in% names(top10S.names)) #new phyloseq object at top 20 ASVs

```

Convert to relative abundance
```{r}
ps_species_Palm_SF10 <- top10S %>%
  tax_glom(taxrank = "Species") %>%                     # agglomerate at species level
  transform_sample_counts(function(x) {x/sum(x)} ) %>% # Transform to rel. abundance
  psmelt() %>%                                         # Melt to long format
  filter(Abundance > 0.01) %>%                         # Filter out low abundance taxa
  arrange(Species) 
```

```{r}

ggplot(ps_species_Palm_SF10, aes(x = Sample_Name, y = Abundance, fill = Species)) +
  geom_bar(stat = "identity", position = "fill") + #width is individual bar width
  facet_wrap(~FirstBM, scales = "free_x") +
  scale_fill_manual(values = getPalette(colourCount)) +
  # Remove x axis title and axis ticks
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
  theme(panel.border = element_blank(),
    panel.background = element_blank()) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  labs(x = 'Samples', y = "Relative Abundance", fill = "Top 10 Genera") +
  ggtitle("Genera Composition Across Capira")
  #theme(legend.position = "none")
```

#Age
##Phyla
Prune to top 20 phyla - using rpal_field
```{r}

top10P.names = sort(tapply(taxa_sums(rpal_field), tax_table(rpal_field)[, "Phylum"], sum), TRUE)[1:10]
#Cut down the physeq.tree data to only the top 10 Genus
top10P = subset_taxa(rpal_field, Phylum %in% names(top10P.names)) #new phyloseq object at top 20 genera

```


Convert to relative abundance
```{r}
ps_phylum <- top10P %>%
  tax_glom(taxrank = "Phylum") %>%                     # agglomerate at genus level
  transform_sample_counts(function(x) {x/sum(x)} ) %>% # Transform to rel. abundance
  psmelt() %>%                                         # Melt to long format
  filter(Abundance > 0.01) %>%                         # Filter out low abundance taxa
  arrange(Phylum) 
```

Re-Set color scale for graph
```{r}
#display.brewer.all(n=NULL, type="all", select=NULL, exact.n=TRUE,
#colorblindFriendly=TRUE)

colourCount <- 10 # max number of categories you need (10 because we are looking at top 10 genera)
getPalette <- colorRampPalette(brewer.pal(10, "Paired")) # 10 is for the number of distinct colors to use, and 12 is the most for "Paired"

```

All Samples
Relative abundance of top 10 genus 
```{r}

phyla_barplot <- ggplot(ps_phylum, aes(x = Sample_Name, y = Abundance, fill = Phylum)) + 
  geom_bar(stat = "identity", position = "fill", width = .8) + #width is individual bar width
  scale_fill_manual(values = getPalette(colourCount)) +
  # Remove x axis title and axis ticks
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
  theme(panel.border = element_blank(),
    panel.background = element_blank()) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  #scale_color_manual(breaks=c('Sphingomonas', 'Erwinia', 'Stenotrophomonas', 'Delftia', "Dietzia", "Staphylococcus", "Pseudomonas", "Corynebacterium", "Enterobacter", "Streptococcus")) +
  labs(x = 'Samples', y = "Relative Abundance", fill = "Top Phyla") +
  ggtitle("Genera Composition Across Samples") 
  #theme(legend.position = "none")
```


Genus Relative Abundance
All samples, Region, and Habitat
Prune to top 20 genera - using rpal_field
```{r}

top10G.names = sort(tapply(taxa_sums(rpal_field), tax_table(rpal_field)[, "Genus"], sum), TRUE)[1:10]
#Cut down the physeq.tree data to only the top 10 Genus
top10G = subset_taxa(rpal_field, Genus %in% names(top10G.names)) #new phyloseq object at top 20 genera

```

Convert to relative abundance
```{r}
ps_genus <- top10G %>%
  tax_glom(taxrank = "Genus") %>%                     # agglomerate at genus level
  transform_sample_counts(function(x) {x/sum(x)} ) %>% # Transform to rel. abundance
  psmelt() %>%                                         # Melt to long format
  filter(Abundance > 0.01) %>%                         # Filter out low abundance taxa
  arrange(Genus) 
```

Re-Set color scale for graph
```{r}
#display.brewer.all(n=NULL, type="all", select=NULL, exact.n=TRUE,
#colorblindFriendly=TRUE)

colourCount <- 10 # max number of categories you need (10 because we are looking at top 10 genera)
getPalette <- colorRampPalette(brewer.pal(10, "Paired")) # 10 is for the number of distinct colors to use, and 12 is the most for "Paired"

```

All Samples
Relative abundance of top 10 genus 
```{r}

ggplot(ps_genus, aes(x = Sample_Name, y = Abundance, fill = Genus)) + 
  geom_bar(stat = "identity", position = "fill", width = 5) + #width is individual bar width
  facet_grid(~Age_Group) +
  scale_fill_manual(values = getPalette(colourCount)) +
  # Remove x axis title and axis ticks
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
  theme(panel.border = element_blank(),
    panel.background = element_blank()) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  scale_color_manual(breaks=c('Sphingomonas', 'Erwinia', 'Stenotrophomonas', 'Delftia', "Dietzia", "Staphylococcus", "Pseudomonas", "Corynebacterium", "Enterobacter", "Streptococcus")) +
  labs(x = 'Samples', y = "Relative Abundance", fill = "Top 10 Genera") +
  ggtitle("Genera Composition Across Samples") 
  #theme(legend.position = "none")
```

Count data for top 10 genera
```{r}
TGroup <- tax_glom(top10G, taxrank = "Genus")
PGroup <- transform_sample_counts(TGroup, function(x)100* x / sum(x))
OTUg <- otu_table(PGroup)
TAXg <- tax_table(PGroup)[,"Genus"]
AverageD <- as.data.frame(rowMeans(OTUg))
names(AverageD) <- c("Mean")
GTable <- merge(TAXg, AverageD, by=0, all=TRUE)
GTable$Row.names = NULL
GTable <- GTable[order(desc(GTable$Mean)),]
head(GTable)
```


##Species level
```{r}

################
# to view all species, not just the top ones

ALLSpecies.names = sort(tapply(taxa_sums(rpal_field), tax_table(rpal_field)[, "Species"], sum), TRUE)

#Cut down the physeq.tree data to only the top 20 species
ALLSpecies = subset_taxa(rpal_field, Species %in% names(ALLSpecies.names)) #new phyloseq object at top 20 ASVs

#######################

top10S.names = sort(tapply(taxa_sums(rpal_field), tax_table(rpal_field)[, "Species"], sum), TRUE)[1:10]
#Cut down the physeq.tree data to only the top 10 species
top10S = subset_taxa(rpal_field, Species %in% names(top10S.names)) #new phyloseq object at top 20 ASVs

```

Convert to relative abundance
```{r}

##### for all species, not just top ones
ps_species_ALL <- ALLSpecies %>%
  tax_glom(taxrank = "Species") %>%                     # agglomerate at species level
  transform_sample_counts(function(x) {x/sum(x)} ) %>% # Transform to rel. abundance
  psmelt() %>%                                         # Melt to long format
  filter(Abundance > 0.01) %>%                         # Filter out low abundance taxa
  arrange(Species)

###########

ps_species <- top10S %>%
  tax_glom(taxrank = "Species") %>%                     # agglomerate at species level
  transform_sample_counts(function(x) {x/sum(x)} ) %>% # Transform to rel. abundance
  psmelt() %>%                                         # Melt to long format
  filter(Abundance > 0.01) %>%                         # Filter out low abundance taxa
  arrange(Species) 
```

write out csv of ASV table for species of all samples
```{r}
write_csv(ps_species_ALL, "ASV_Table_allSpecies.csv")

```


Re-Set color scale for graph
```{r}
#display.brewer.all(n=NULL, type="all", select=NULL, exact.n=TRUE,
#colorblindFriendly=TRUE)

colourCount <- 10 # max number of categories you need (10 because we are looking at top 10 genera)
getPalette <- colorRampPalette(brewer.pal(10, "Paired")) # 10 is for the number of distinct colors to use, and 12 is the most for "Paired"

```

All Samples
Relative abundance of top 10 genus 
```{r}

species_barplot <- ggplot(ps_species, aes(x = Sample_Name, y = Abundance, fill = Species)) +
  geom_bar(stat = "identity", position = "fill") + #width is individual bar width
  scale_fill_manual(values = getPalette(colourCount)) +
  # Remove x axis title and axis ticks
  theme(axis.text.x = element_blank(), axis.ticks = element_blank()) + 
    theme(plot.title = element_text(size = 12, hjust = 0.5, face = "bold")) +
  theme(panel.border = element_blank(),
    panel.background = element_blank()) +
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  scale_color_manual(breaks=c('Sphingomonas', 'Erwinia', 'Stenotrophomonas', 'Delftia', "Dietzia", "Staphylococcus", "Pseudomonas", "Corynebacterium", "Enterobacter", "Streptococcus")) +
  labs(x = 'Samples', y = "Relative Abundance", fill = "Top 10 Genera") +
  ggtitle("Genera Composition Across Samples")
  #theme(legend.position = "none")
```

Count data for top 20 species
```{r}
TGroup <- tax_glom(top20S, taxrank = "Species")
PGroup <- transform_sample_counts(TGroup, function(x)100* x / sum(x))
OTUg <- otu_table(PGroup)
TAXg <- tax_table(PGroup)[,"Species"]
AverageD <- as.data.frame(rowMeans(OTUg))
names(AverageD) <- c("Mean")
GTable <- merge(TAXg, AverageD, by=0, all=TRUE)
GTable$Row.names = NULL
GTable <- GTable[order(desc(GTable$Mean)),]
head(GTable)
```

