---
title: "MixedModels_March2023"
author: "Kaylee Arnold"
date: "2023-03-13" "Updated Feb 16 2024"
output: html_document
---

#load libraries

```{r}
library(lmerTest)
library(car)
library(lme4)
library(MuMIn)
library(DHARMa)
library(corrr)
library(ggcorrplot)
```


Variation in gut microbiome diversity and composition across region
GLMM ** Will use poisson for Observed data (integers) and Gamma for Faith and Shannon (non-integers)


Test for normality
```{r}
library(ggpubr)

#Density Plot
ggdensity(adiv_all_variables_BM$Shannon, fill = "lightgray")
# QQ plot
ggqqplot(adiv_all_variables_BM$Shannon)

shapiro.test(adiv_all_variables_BM$Shannon) #significant - data non normal

```



We already know alpha is split by region (Veraguas v Canal) and age group (N1-N3 v N4-adult). Now, what drives these differences other than just these variables (if any)

#Shannon diversity (alpha)
##Veraguas N4-adult 
```{r}
library(lmerTest)
library(car)
library(lme4)
library(MuMIn)
library(DHARMa)


null_mod1 <- glmer(Shannon ~ (1 | PalmID), data = adiv_all_variables_veraguas_N4Adult, family = Gamma(link = "inverse")) #null model only includes the fixed effects 

full_mod1a <- glmer(Shannon ~ Habitat + SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = Gamma(link = "inverse"))

full_mod1b <- glmer(Shannon ~ Habitat * SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = Gamma(link = "inverse")) #infection and habitat highly correlated in interaction effect

full_mod1c <- glmer(Shannon ~ Habitat + SingleInf_Tcruzi * TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = Gamma(link = "inverse"))

mod1a <- glmer(Shannon ~ Habitat + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = Gamma(link = "inverse"))

mod1b <- glmer(Shannon ~ SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = Gamma(link = "inverse")) 

mod1c <- glmer(Shannon ~ TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = Gamma(link = "inverse")) #best fit

mod1d <- glmer(Shannon ~ Habitat + SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = Gamma(link = "inverse"))

mod1e <- glmer(Shannon ~ Habitat * SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = Gamma(link = "inverse"))

mod1f <- glmer(Shannon ~ Habitat + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = Gamma(link = "inverse"))

mod1g <- glmer(Shannon ~ Habitat * TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = Gamma(link = "inverse"))

mod1h <- glmer(Shannon ~ SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = Gamma(link = "inverse")) #best fit



AIC(null_mod1, full_mod1a,full_mod1b,full_mod1c,mod1a,mod1b,mod1c, mod1d,mod1e,mod1f,mod1g,mod1h)

```

##Canal N4 Adult
```{r}
null_mod2 <- glmer(Shannon ~ (1 | PalmID), data = adiv_all_variables_N4Adult_canal, family = Gamma(link = "inverse")) #null model only includes the fixed effects 

full_mod2a <- glmer(Shannon ~ Habitat + SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = Gamma(link = "inverse")) #doesn't converge

full_mod2b <- glmer(Shannon ~ Habitat * SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = Gamma(link = "inverse"))

full_mod2c <- glmer(Shannon ~ Habitat + SingleInf_Tcruzi * TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = Gamma(link = "inverse"))


mod2a <- glmer(Shannon ~ Habitat + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = Gamma(link = "inverse"))

mod2b <- glmer(Shannon ~ SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = Gamma(link = "inverse")) #

mod2c <- glmer(Shannon ~ TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = Gamma(link = "inverse"))


mod2d <- glmer(Shannon ~ Habitat + SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = Gamma(link = "inverse"))

mod2e <- glmer(Shannon ~ Habitat * SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = Gamma(link = "inverse"))

mod2f <- glmer(Shannon ~ Habitat + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = Gamma(link = "inverse"))

mod2g <- glmer(Shannon ~ Habitat * TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = Gamma(link = "inverse"))

mod2h <- glmer(Shannon ~ SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = Gamma(link = "inverse"))




AIC(null_mod2,full_mod2a,full_mod2b,full_mod2c,mod2a,mod2b,mod2c, mod2d,mod2e,mod2f,mod2g,mod2h)


```



## Veraguas N1 N3
```{r}
null_mod3 <- glmer(Shannon ~ (1 | PalmID), data = adiv_all_variables_veraguas_N1N3, family = Gamma(link = "inverse")) #null model only includes the fixed effects 

full_mod3a <- glmer(Shannon ~ Habitat + SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = Gamma(link = "inverse")) #Only mammals

full_mod3b <- glmer(Shannon ~ Habitat * SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = Gamma(link = "inverse"))

full_mod3c <- glmer(Shannon ~ Habitat + SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = Gamma(link = "inverse"))


mod3a <- glmer(Shannon ~ Habitat + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = Gamma(link = "inverse"))

mod3b <- glmer(Shannon ~ SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = Gamma(link = "inverse")) 

#mod3c <- glmer(Shannon ~ TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = Gamma(link = "inverse"))

mod3d <- glmer(Shannon ~ Habitat + SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = Gamma(link = "inverse"))

mod3e <- glmer(Shannon ~ Habitat * SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = Gamma(link = "inverse"))

#mod3f <- glmer(Shannon ~ Habitat + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = Gamma(link = "inverse"))

#mod3g <- glmer(Shannon ~ Habitat * TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = Gamma(link = "inverse"))

#mod3h <- glmer(Shannon ~ SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = Gamma(link = "inverse"))


AIC(null_mod3,full_mod3a,full_mod3b,mod3a,mod3b, mod3d,mod3e)

```


## Canal N1 N3
```{r}
null_mod4 <- glmer(Shannon ~ (1 | PalmID), data = adiv_all_variables_N1N3_canal, family = Gamma(link = "inverse")) #null model only includes the fixed effects 

full_mod4a <- glmer(Shannon ~ Habitat + SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = Gamma(link = "inverse")) 

full_mod4b <- glmer(Shannon ~ Habitat * SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = Gamma(link = "inverse"))

full_mod4c <- glmer(Shannon ~ Habitat + SingleInf_Tcruzi * TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = Gamma(link = "inverse")) #does not converge


mod4a <- glmer(Shannon ~ Habitat + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = Gamma(link = "inverse"))

mod4b <- glmer(Shannon ~ SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = Gamma(link = "inverse")) 

mod4c <- glmer(Shannon ~ TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = Gamma(link = "inverse"))


mod4d <- glmer(Shannon ~ Habitat + SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = Gamma(link = "inverse"))

mod4e <- glmer(Shannon ~ Habitat * SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = Gamma(link = "inverse"))

mod4f <- glmer(Shannon ~ Habitat + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = Gamma(link = "inverse"))

mod4g <- glmer(Shannon ~ Habitat * TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = Gamma(link = "inverse"))

mod4h <- glmer(Shannon ~ SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = Gamma(link = "inverse"))




AIC(null_mod4,full_mod4a,full_mod4b,full_mod4c,mod4a,mod4b,mod4c, mod4d,mod4e,mod4f,mod4g,mod4h)

```



# Observed
## Veraguas N4 Adult
```{r}
library(lmerTest)
library(car)
library(lme4)
library(MuMIn)
library(DHARMa)


null_mod5 <- glmer(Observed ~ (1 | PalmID), data = adiv_all_variables_veraguas_N4Adult, family = poisson(link = "log")) #null model only includes the fixed effects 

full_mod5a <- glmer(Observed ~ Habitat + SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = poisson(link = "log"))

full_mod5b <- glmer(Observed ~ Habitat * SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = poisson(link = "log"))

full_mod5b <- glmer(Observed ~ Habitat + SingleInf_Tcruzi * TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = poisson(link = "log"))


mod5a <- glmer(Observed ~ Habitat + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = poisson(link = "log"))

mod5b <- glmer(Observed ~ SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = poisson(link = "log")) 

mod5c <- glmer(Observed ~ TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = poisson(link = "log"))


mod5d <- glmer(Observed ~ Habitat + SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = poisson(link = "log"))

mod5e <- glmer(Observed ~ Habitat * SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = poisson(link = "log"))

mod5f <- glmer(Observed ~ Habitat + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = poisson(link = "log"))

mod5g <- glmer(Observed ~ Habitat * TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = poisson(link = "log"))

mod5h <- glmer(Observed ~ SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N4Adult, family = poisson(link = "log"))




AIC(null_mod5, full_mod5a,full_mod5b,mod5a,mod5b,mod5c, mod5d,mod5e,mod5f,mod5g,mod5h)

```

##Canal N4 Adult
```{r}
null_mod6 <- glmer(Observed ~ (1 | PalmID), data = adiv_all_variables_N4Adult_canal, family = poisson(link = "log")) #null model only includes the fixed effects 

full_mod6a <- glmer(Observed ~ Habitat + SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = poisson(link = "log")) #doesn't converge

full_mod6b <- glmer(Observed ~ Habitat * SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = poisson(link = "log"))

full_mod6c <- glmer(Observed ~ Habitat + SingleInf_Tcruzi * TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = poisson(link = "log"))


mod6a <- glmer(Observed ~ Habitat + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = poisson(link = "log"))

mod6b <- glmer(Observed ~ SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = poisson(link = "log")) ## best fit model -- infection drives alpha differences

mod6c <- glmer(Observed ~ TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = poisson(link = "log"))


mod6d <- glmer(Observed ~ Habitat + SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = poisson(link = "log"))

mod6e <- glmer(Observed ~ Habitat * SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = poisson(link = "log"))

mod6f <- glmer(Observed ~ Habitat + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = poisson(link = "log"))

mod6g <- glmer(Observed ~ Habitat * TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = poisson(link = "log"))

mod6h <- glmer(Observed ~ SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N4Adult_canal, family = poisson(link = "log"))




AIC(null_mod6,full_mod6a,mod6a,mod6b,mod6c, mod6d,mod6e,mod6f,mod6g,mod6h)

```



## Veraguas N1 N3
```{r}
null_mod7 <- glmer(Observed ~ (1 | PalmID), data = adiv_all_variables_veraguas_N1N3, family = Gamma(link = "inverse")) #null model only includes the fixed effects 

full_mod7a <- glmer(Observed ~ Habitat + SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = poisson(link = "log")) 

full_mod7b <- glmer(Observed ~ Habitat * SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = poisson(link = "log"))

full_mod7c <- glmer(Observed ~ Habitat + SingleInf_Tcruzi * TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = poisson(link = "log"))


mod7a <- glmer(Observed ~ Habitat + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = poisson(link = "log"))

mod7b <- glmer(Observed ~ SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = poisson(link = "log"))

mod7c <- glmer(Observed ~ TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = poisson(link = "log"))


mod7d <- glmer(Observed ~ Habitat + SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = poisson(link = "log"))

mod7e <- glmer(Observed ~ Habitat * SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = poisson(link = "log"))

mod7f <- glmer(Observed ~ Habitat + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = poisson(link = "log"))

mod7g <- glmer(Observed ~ Habitat * TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = poisson(link = "log"))

mod7h <- glmer(Observed ~ SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_veraguas_N1N3, family = poisson(link = "log"))



AIC(null_mod7,full_mod7a,full_mod7b,full_mod7c,mod7a,mod7b,mod7c, mod7d,mod7e,mod7f,mod7g,mod7h)

```


## Canal N1 N3 obserevd
```{r}
null_mod8 <- glmer(Observed ~ (1 | PalmID), data = adiv_all_variables_N1N3_canal, family = poisson(link = "log")) #null model only includes the fixed effects 

full_mod8a <- glmer(Observed ~ Habitat + SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = poisson(link = "log")) 

full_mod8b <- glmer(Observed ~ Habitat * SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = poisson(link = "log"))

full_mod8c <- glmer(Observed ~ Habitat + SingleInf_Tcruzi * TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = poisson(link = "log")) #does not converge


mod8a <- glmer(Observed ~ Habitat + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = poisson(link = "log"))

mod8b <- glmer(Observed ~ SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = poisson(link = "log")) 

mod8c <- glmer(Observed ~ TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = poisson(link = "log"))


mod8d <- glmer(Observed ~ Habitat + SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = poisson(link = "log"))

mod8e <- glmer(Observed ~ Habitat * SingleInf_Tcruzi + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = poisson(link = "log"))

mod8f <- glmer(Observed ~ Habitat + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = poisson(link = "log"))

mod8g <- glmer(Observed ~ Habitat * TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = poisson(link = "log"))

mod8h <- glmer(Observed ~ SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=adiv_all_variables_N1N3_canal, family = poisson(link = "log"))


AIC(null_mod8,full_mod8b,mod8a,mod8b,mod8c, mod8d,mod8e,mod8f,mod8g,mod8h)

```

# Faith
##Veraguas N4 - Adult
```{r}

null_mod9 <- glmer(faith_pd ~ (1 | PalmID), data = FaithBM_Veraguas_N4Adult, family = Gamma(link = "inverse")) #null model only includes the fixed effects 

full_mod9a <- glmer(faith_pd ~ Habitat + SingleInf_Tcruzi + TypeBM_Updated_Updated + (1 | PalmID), data=FaithBM_Veraguas_N4Adult, family = Gamma(link = "inverse")) #does not converge

full_mod9b <- glmer(faith_pd ~ Habitat * SingleInf_Tcruzi + TypeBM_Updated_Updated + (1 | PalmID), data=FaithBM_Veraguas_N4Adult, family = Gamma(link = "inverse")) # does not converge

full_mod9c <- glmer(faith_pd ~ Habitat + SingleInf_Tcruzi * TypeBM_Updated_Updated + (1 | PalmID), data=FaithBM_Veraguas_N4Adult, family = Gamma(link = "inverse"))


mod9a <- glmer(faith_pd ~ Habitat + (1 | PalmID), data=FaithBM_Veraguas_N4Adult, family = Gamma(link = "inverse"))

mod9b <- glmer(faith_pd ~ SingleInf_Tcruzi + (1 | PalmID), data=FaithBM_Veraguas_N4Adult, family = Gamma(link = "inverse")) ## best fit model -- infection drives alpha differences

mod9c <- glmer(faith_pd ~ TypeBM_Updated_Updated + (1 | PalmID), data=FaithBM_Veraguas_N4Adult, family = Gamma(link = "inverse"))


mod9d <- glmer(faith_pd ~ Habitat + SingleInf_Tcruzi + (1 | PalmID), data=FaithBM_Veraguas_N4Adult, family = Gamma(link = "inverse"))

mod9e <- glmer(faith_pd ~ Habitat * SingleInf_Tcruzi + (1 | PalmID), data=FaithBM_Veraguas_N4Adult, family = Gamma(link = "inverse"))

mod9f <- glmer(faith_pd ~ Habitat + TypeBM_Updated + (1 | PalmID), data=FaithBM_Veraguas_N4Adult, family = Gamma(link = "inverse"))

mod9g <- glmer(faith_pd ~ Habitat * TypeBM_Updated + (1 | PalmID), data=FaithBM_Veraguas_N4Adult, family = Gamma(link = "inverse"))

mod9h <- glmer(faith_pd ~ SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=FaithBM_Veraguas_N4Adult, family = Gamma(link = "inverse"))


AIC(null_mod9, full_mod9a,full_mod9b,full_mod9c,mod9a,mod9b,mod9c, mod9d,mod9e,mod9f,mod9g,mod9h)
```


## Canal N4 Adult - Faith
```{r}

null_mod10 <- glmer(faith_pd ~ (1 | PalmID), data = FaithBM_Canal_N4Adult, family = Gamma(link = "inverse")) #null model only includes the fixed effects 

full_mod10a <- glmer(faith_pd ~ Habitat + SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=FaithBM_Canal_N4Adult, family = Gamma(link = "inverse"))

full_mod10b <- glmer(faith_pd ~ Habitat * SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=FaithBM_Canal_N4Adult, family = Gamma(link = "inverse")) # does not converge

full_mod10c <- glmer(faith_pd ~ Habitat + SingleInf_Tcruzi * TypeBM_Updated + (1 | PalmID), data=FaithBM_Canal_N4Adult, family = Gamma(link = "inverse"))


mod10a <- glmer(faith_pd ~ Habitat + (1 | PalmID), data=FaithBM_Canal_N4Adult, family = Gamma(link = "inverse"))

mod10b <- glmer(faith_pd ~ SingleInf_Tcruzi + (1 | PalmID), data=FaithBM_Canal_N4Adult, family = Gamma(link = "inverse")) ## best fit model -- infection drives alpha differences

mod10c <- glmer(faith_pd ~ TypeBM_Updated + (1 | PalmID), data=FaithBM_Canal_N4Adult, family = Gamma(link = "inverse"))


mod10d <- glmer(faith_pd ~ Habitat + SingleInf_Tcruzi + (1 | PalmID), data=FaithBM_Canal_N4Adult, family = Gamma(link = "inverse"))

mod10e <- glmer(faith_pd ~ Habitat * SingleInf_Tcruzi + (1 | PalmID), data=FaithBM_Canal_N4Adult, family = Gamma(link = "inverse"))

mod10f <- glmer(faith_pd ~ Habitat + TypeBM_Updated + (1 | PalmID), data=FaithBM_Canal_N4Adult, family = Gamma(link = "inverse")) # does not converege

mod10g <- glmer(faith_pd ~ Habitat * TypeBM_Updated + (1 | PalmID), data=FaithBM_Canal_N4Adult, family = Gamma(link = "inverse"))

mod10h <- glmer(faith_pd ~ SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=FaithBM_Canal_N4Adult, family = Gamma(link = "inverse"))




AIC(null_mod10, full_mod10a,full_mod10b,full_mod10c,mod10a,mod10b,mod10c, mod10d,mod10e,mod10f,mod10g,mod10h)
```

##Veraguas N1 N3 - Faith
```{r}

null_mod11 <- glmer(faith_pd ~ (1 | PalmID), data = FaithBM_Veraguas_N1N3, family = Gamma(link = "inverse")) #null model only includes the fixed effects 

full_mod11a <- glmer(faith_pd ~ Habitat + SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=FaithBM_Veraguas_N1N3, family = Gamma(link = "inverse"))

full_mod11b <- glmer(faith_pd ~ Habitat * SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=FaithBM_Veraguas_N1N3, family = Gamma(link = "inverse")) # does not converge

full_mod11c <- glmer(faith_pd ~ Habitat + SingleInf_Tcruzi * TypeBM_Updated + (1 | PalmID), data=FaithBM_Veraguas_N1N3, family = Gamma(link = "inverse"))


mod11a <- glmer(faith_pd ~ Habitat + (1 | PalmID), data=FaithBM_Veraguas_N1N3, family = Gamma(link = "inverse"))

mod11b <- glmer(faith_pd ~ SingleInf_Tcruzi + (1 | PalmID), data=FaithBM_Veraguas_N1N3, family = Gamma(link = "inverse")) ## best fit model -- infection drives alpha differences

mod11c <- glmer(faith_pd ~ TypeBM_Updated + (1 | PalmID), data=FaithBM_Veraguas_N1N3, family = Gamma(link = "inverse"))


mod11d <- glmer(faith_pd ~ Habitat + SingleInf_Tcruzi + (1 | PalmID), data=FaithBM_Veraguas_N1N3, family = Gamma(link = "inverse"))

mod11e <- glmer(faith_pd ~ Habitat * SingleInf_Tcruzi + (1 | PalmID), data=FaithBM_Veraguas_N1N3, family = Gamma(link = "inverse"))

mod11f <- glmer(faith_pd ~ Habitat + TypeBM_Updated + (1 | PalmID), data=FaithBM_Veraguas_N1N3, family = Gamma(link = "inverse")) 

mod11g <- glmer(faith_pd ~ Habitat * TypeBM_Updated + (1 | PalmID), data=FaithBM_Veraguas_N1N3, family = Gamma(link = "inverse"))

mod11h <- glmer(faith_pd ~ SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=FaithBM_Veraguas_N1N3, family = Gamma(link = "inverse"))




AIC(null_mod11, full_mod11a,full_mod11b,full_mod11c,mod11a,mod11b,mod11c, mod11d,mod11e,mod11f,mod11g,mod11h)
```


## Canal N1 N3 Faith
```{r}

null_mod12 <- glmer(faith_pd ~ (1 | PalmID), data = FaithBM_Canal_N1N3, family = Gamma(link = "inverse")) #null model only includes the fixed effects 

full_mod12a <- glmer(faith_pd ~ Habitat + SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=FaithBM_Canal_N1N3, family = Gamma(link = "inverse"))

full_mod12b <- glmer(faith_pd ~ Habitat * SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=FaithBM_Canal_N1N3, family = Gamma(link = "inverse")) # does not converge

full_mod12c <- glmer(faith_pd ~ Habitat + SingleInf_Tcruzi * TypeBM_Updated + (1 | PalmID), data=FaithBM_Canal_N1N3, family = Gamma(link = "inverse"))


mod12a <- glmer(faith_pd ~ Habitat + (1 | PalmID), data=FaithBM_Canal_N1N3, family = Gamma(link = "inverse"))

mod12b <- glmer(faith_pd ~ SingleInf_Tcruzi + (1 | PalmID), data=FaithBM_Canal_N1N3, family = Gamma(link = "inverse")) ## best fit model -- infection drives alpha differences

mod12c <- glmer(faith_pd ~ TypeBM_Updated + (1 | PalmID), data=FaithBM_Canal_N1N3, family = Gamma(link = "inverse"))


mod12d <- glmer(faith_pd ~ Habitat + SingleInf_Tcruzi + (1 | PalmID), data=FaithBM_Canal_N1N3, family = Gamma(link = "inverse"))

mod12e <- glmer(faith_pd ~ Habitat * SingleInf_Tcruzi + (1 | PalmID), data=FaithBM_Canal_N1N3, family = Gamma(link = "inverse"))

mod12f <- glmer(faith_pd ~ Habitat + TypeBM_Updated + (1 | PalmID), data=FaithBM_Canal_N1N3, family = Gamma(link = "inverse")) #does not converege

mod12g <- glmer(faith_pd ~ Habitat * TypeBM_Updated + (1 | PalmID), data=FaithBM_Canal_N1N3, family = Gamma(link = "inverse"))

mod12h <- glmer(faith_pd ~ SingleInf_Tcruzi + TypeBM_Updated + (1 | PalmID), data=FaithBM_Canal_N1N3, family = Gamma(link = "inverse"))

mod13h <- glmer(faith_pd ~ SingleInf_Tcruzi * TypeBM_Updated + (1 | PalmID), data=FaithBM_Canal_N1N3, family = Gamma(link = "inverse"))




AIC(null_mod12, full_mod12a,full_mod12b,full_mod12c,mod12a,mod12b,mod12c, mod12d,mod12e,mod12f,mod12g,mod12h,mod13h)
```